%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Clark Van Oyen} % Your name
\address{704 - 31 Elliot St \\ New Westminster, BC, V3L 5C9} % Your address
\address{(778)~$\cdot$~709~$\cdot$~1230 \\ clark@countable.ca} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Executive Summary}
\item Consulting CTO with depth in end-to-end web/cloud product development.
\item Love developing a shared vision to working prototype, as a methodology to building the best product.
\item Experience with many aspects related to product: Operations, Test, Automation.
\item Enjoy finding solutions in diverse stakeholders' negoatiation.
\end{rSection}

\begin{rSection}{Experience}

% \begin{rSubsection}{Technical Highlights}{}{}{}
% \item Next Gen Telecom Backend - http://otono.com
% \item Agriculure networking site - http://maps.youngagrarians.org
% \item A 3D Car Configurator - http://www.animaticmedia.com/nissanconfigurator/examples/nissan.html
% \item A VR Comic Book - http://www.animaticmedia.com/vr/drstrange/
% \item Medical Devices Cloud - http://cloud.clarius.me
% \end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Countable Web Productions Inc.}{December 2008 - present}{Owner}{New Westminster, BC}
\item Rapid prototyping minimum viable products to gain insight on technical viability and product-market fit.
\item Specialize in unusual web technology deployments, process automation, cloud platform strategy.
\item Developed in-house web product (http://htmlcommentbox.com) now serving over one hundred million visitors per day.
\item Full stack web system design, distributed systems, firmware management, business domain driven design, back-end infrastructure.
\item API integration with mobile apps, sensors / the Internet of Things.
\item Clients list includes Animatic Media (with their clients Nissan, Marvel, Sesame St), Clarius Corporation, Corvus Energy, Kensington Medical, EmerGeo, Altas Realty, Ecotrust Canada, Otono.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Ecotrust Canada}{January 2014 - Jan 2016}{(Consulting) Chief Technology Officer}{Vancouver, BC}
\item Developed original core technology of Ecotrust Canada's traceability and electronic monitoring programs, now a seven figure business with dedicated teams.
\item Technology direction for products: monitor emergent technology opportunities; source and mentors technical staff; Contributes technology related strategy and planning, grant and SRED applications, budgeting, licensing, certification and reporting.
\item Design of architecture, technology lifecycles, testing and implementation.
\end{rSubsection}

%-----------------------------------------------

\begin{rSubsection}{Redback Networks / Ericsson}{December 2006 - 2007}{ATM Protocol Developer}{Burnaby, BC}
\item Contributed to the ATM protocol stack in a carrier class router. Developed test coverage tools, worked through a backlog of bugs that spanned other teams’ modules.
\item Refactored ATM module codebase to address issues found by a static analysis tool.

\end{rSubsection}
\begin{rSubsection}{Convedia / Radisys}{December 2005 - 2006}{Automation Specialist, SIP Developer}{Burnaby, BC}
\item Developed an automated test manager that configured and utilized a lab full of carrier class computing hardware at night when otherwise idle, to test embedded media server product and report results through flexible web visualizations.
\item Wrote the unit test suite for a 3rd party SIP stack integrated by our media server. Contributed to a test harness for the media server product.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Selected Tools}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & Javascript, AWK, HTML, CSS, jade, stylus, OpenGL, \\
 & MATLAB, TCL, C, C++, Basic (various), ASP, C\#, Java, \\
 & Python, Node.JS, PHP, R, CoffeeScript \\
Protocols & HTTP, TCP, XML, JSON, SOAP, REST \\
Databases & MySQL, PostgreSQL, Microsoft SQL, MongoDB, Redis, SQLite \\
OS / Platforms & (developed under) Windows, Linux, OSX, BSD, lynxos, Android, Arduino \\
Frameworks & Django, Express, Flask, Wordpress, jQuery, Backbone, Angular, ExtJS, (custom) \\
Other & GIT, SVN, AWS, Google App Engine, Scrum \\
\end{tabular}
\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Selected Open Source}

\begin{rSubsection}{Through Ecotrust Canada GitHub}{https://github.com/Ecotrust-Canada}{}{}
\item Hypochondriapp - Canadian Open Data Experience hackathon entry, see \newline
http://ecotrust-canada.github.io/hypochondriapp/ for a working version.
\item Terratruth - A spatial referral management and decision support tool.
\item EM Control Box - A remote sensing "firmware" for commercial fishery monitoring (runs in custom embedded linux).
\end{rSubsection}

\begin{rSubsection}{Through Countable GitHub}{https://github.com/countable}{}{}
\item node-dogecoin - Maintainer for the Node.JS Dogecoin (cryptocurrency) API.
\item js-fdf - Maintainer for the Node.JS FDF implementation.
\item Kinect3D - 3d version of Microsoft Kinect API sandbox using WPF 3d objects.
\item (forks) - Contributed fixes, features, tests to several bigger OSS projects.
\end{rSubsection}


\end{rSection}

%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
% EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of British Columbia} \hfill {\em 2008} \\ 
B.S. in Computer Science \& Physics \\
Completed Co-op, Awarded NSERC \\

{\bf Canadian Association of Physicists} \hfill {\em 2003} \\ 
Top 15th percentile in CAP Prize Exam \\

{\bf Gulf Islands Film and TV School} \hfill {\em 2002} \\ 
Classical Animation Certificate \\

\end{rSection}

%----------------------------------------------------------------------------------------
% PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Publications}

{\bf Operationalizing Open-Source Electronic Monitoring Systems in New England Groundfish Sectors} \hfill {\em 2014} \\ 
Fisheries Bycatch: Global Issues and Creative Solutions, Contributor \\

{\bf Interoperable Seafood Traceability Technology Architecture Issues Brief 11.6.15} \hfill {\em 2014} \\ 
GFTC, IFT Publication, Contributor \\

\end{rSection}

\end{document}

